---
title: "Exploratory Data Analysis (EDA)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE }
library(tidyverse)
```



## Team Members
- Brenden Everitt 
- Miliban Keyim  
- Maninder Kohli 
- Phuntsok Tseten  


## Survey Questions Being Explored

  - Q1 What is your preffered language to use when doing data analysis?
  - Q2 What is the first computing language you learned?
  - Q3 What was your undergraduate degree in?
  - Q4 What is the typical size of your analysis projects? Small(10K rows), Medium(10-1M rows), or large (1m+ rows)?
  - Q5 Which language do you think has better documentation when it comes to its data analysis packages?


## Exploratory Data Analysis (EDA)

Importing Data and Data Wrangling

```{r, include=FALSE}
# Import data
raw <- read_csv("https://raw.github.ubc.ca/MDS-2018-19/DSCI_554_R2Py2_results/master/DSCI_554_R2Py2.csv?token=AAAGiR15X4PWpGVkb0ojAtjTWSq1Sppwks5csTi9wA%3D%3D")


# Data wrangle 
survey <- raw %>% 
  slice(-c(1:2)) %>% 
  select(contains("Q")) %>% 
  mutate(Q4=str_extract(Q4, "(^[A-Za-z]+)")) %>% 
  mutate(Q1 = as.factor(Q1),
         Q2 = as.factor(Q2),
         Q3 = as.factor(Q3),
         Q4 = as.factor(Q4),
         Q5 = as.factor(Q5))

survey <- as.data.frame(survey)
```

## Analyzing Summary Data

Summary of all survey data 
```{r}
survey_summary <- summary(survey)
survey_summary

```

Q1 What is your preffered language to use when doing data analysis?
```{r}

q1 <- table(survey$Q1)
q1 <- round(prop.table(q1), digits=2)
q1  

```
65% of respondents preferred using Python vs R for data analysis. 


Q2 What is the first computing language you learned?
```{r}

q2 <- table(survey$Q2)
q2 <- round(prop.table(q2), digits=2)
q2  

```
Majority of the survey respondents were split between C/C++/C#, Other and Python at 20% as the first programming language used.


Q3 What was your undergraduate degree in?
```{r}

q3 <- table(survey$Q3)
q3 <- round(prop.table(q3), digits=2)
q3  

```
50% of the respondents had an undergraduate degree in either Math/Statstics or Other Science at 25% each.


Q4 What is the typical size of your analysis projects? Small(10K rows), Medium(10-1M rows), or large (1m+ rows)?
```{r}

q4 <- table(survey$Q4)
q4 <- round(prop.table(q4), digits=2)
q4  

```
Over half of the respondents had experience with small analysis projects.


Q5 Which language do you think has better documentation when it comes to its data analysis packages?
```{r}

q5 <- table(survey$Q5)
q5 <- round(prop.table(q5), digits=2)
q5  

```
A large proportion of respondents (64%) believed Python had better documentation.




## Plots



```{r plots, echo = FALSE}
#plots
survey %>% ggplot(aes(x = Q1)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), width = 0.5, fill = 'salmon') +
  geom_text(aes(y = ((..count..)/sum(..count..)),
                label = scales::percent((..count..)/sum(..count..))),
            stat = "count", vjust = -0.25, width = 0.5) +
  theme_bw() +
  labs(title = 'Which Language is more prefered for Data Analysis?',
       x = 'Language',
       y='%') 

# More people prefer python

survey %>% ggplot(aes(x = Q2)) +
  geom_bar(aes(fill = Q1), stat = 'count') +
  theme_bw() +
  scale_fill_discrete("Prefers:") +
  labs(title = "What was the first computing language you learned?",
       x = 'Language',
       y = 'Count')+
  coord_flip()

#Those that learned Java/Javascript/HTML/CSS seem to all prefer python over R

survey %>% ggplot(aes(x = Q3)) +
  geom_bar(aes(fill = Q1), stat = 'count') +
  theme_bw() +
  scale_fill_discrete("Prefers:") +
  labs(title = "What is your undergraduate degree in?",
       x = 'Major',
       y = 'Count')

#Those with a CS background always prefer Python, those with Sciences/Other degrees seem to prefer R over Python. 

survey %>% ggplot(aes(x = Q4)) +
  geom_bar(aes(fill = Q1), stat = 'count') +
  theme_bw() +
  scale_fill_discrete("Prefers:") +
  labs(title = "What is the size of your typical data set?",
       x = 'Size',
       y = 'Count')

#It seems more people prefer python no matter the size of the data set

survey %>% ggplot(aes(x = Q5)) +
  geom_bar(aes(fill = Q1), stat = 'count') +
  theme_bw() +
  scale_fill_discrete("Prefers:") +
  labs(title = "Which language has better documentation of data analysis packages??",
       x = 'Language',
       y = 'Count')

# It seems highly correlated that people prefer to choose the language that they believe has better documentation.

```


