---
title: "Exploratory Data Analysis (EDA)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE }
library(tidyverse)

```



## Team Members
- Brenden Everitt 
- Miliban Keyim  
- Maninder Kohli 
- Phuntsok Tseten  


## Survey Questions Being Explored

  - Q1 What is your preffered language to use when doing data analysis?
  - Q2 What is the first computing language you learned?
  - Q3 What was your undergraduate degree in?
  - Q4 What is the typical size of your analysis projects? Small(10K rows), Medium(10-1M rows), or large (1m+ rows)?
  - Q5 Which language do you think has better documentation when it comes to its data analysis packages?


## Exploratory Data Analysis (EDA)

Importing Data and Data Wrangling

```{r, include=FALSE}
# Import data
raw <- read_csv("https://raw.github.ubc.ca/MDS-2018-19/DSCI_554_R2Py2_results/master/DSCI_554_R2Py2.csv?token=AAAGiR15X4PWpGVkb0ojAtjTWSq1Sppwks5csTi9wA%3D%3D")


# Data wrangle 
survey <- raw %>% 
  slice(-c(1:2)) %>% 
  select(contains("Q")) %>% 
  mutate(Q4=str_extract(Q4, "(^[A-Za-z]+)")) %>% 
  mutate(Q1 = as.factor(Q1),
         Q2 = as.factor(Q2),
         Q3 = as.factor(Q3),
         Q4 = as.factor(Q4),
         Q5 = as.factor(Q5))

survey <- as.data.frame(survey)
```

## Analyzing Summary Data

Summary of all survey data 
```{r}
survey_summary <- summary(survey)
survey_summary

```

Q1 What is your preffered language to use when doing data analysis?
```{r}

q1 <- table(survey$Q1)
q1 <- round(prop.table(q1), digits=2)
q1  

```
65% of respondents preferred using Python vs R for data analysis. 


Q2 What is the first computing language you learned?
```{r}

q2 <- table(survey$Q2)
q2 <- round(prop.table(q2), digits=2)
q2  

```
Majority of the survey respondents were split between C/C++/C#, Other and Python at 20% as the first programming language used.


Q3 What was your undergraduate degree in?
```{r}

q3 <- table(survey$Q3)
q3 <- round(prop.table(q3), digits=2)
q3  

```
50% of the respondents had an undergraduate degree in either Math/Statstics or Other Science at 25% each.


Q4 What is the typical size of your analysis projects? Small(10K rows), Medium(10-1M rows), or large (1m+ rows)?
```{r}

q4 <- table(survey$Q4)
q4 <- round(prop.table(q4), digits=2)
q4  

```
Over half of the respondents had experience with small analysis projects.


Q5 Which language do you think has better documentation when it comes to its data analysis packages?
```{r}

q5 <- table(survey$Q5)
q5 <- round(prop.table(q5), digits=2)
q5  

```
A large propprtion of respondents (64%) though Python had better documentation.




## Plots



```{r pressure, echo=FALSE}
#plots
```


