---
title: "Python vs. R"
date: "April 13, 2019"
output: github_document
---  

```{r, Setup, include=FALSE }
library(tidyverse)
library(broom)
```

### Analysis Question  

Python and R are the two dominate Data Science programming languages, we set out determine how people's background influenced their choice. In particular we wanted to answer the following question:  

> _Does the first programming language learned influence whether someone prefers Python or R when it comes to data analysis?_  

### Potentinal Confounders  

We identified the following potential counfounding variables:  

1. What was your undergraduate degree in?  
    - Someone's educational background could have a large influence on their preferred programming language. 
2. What is the typical size of your analysis projects? Small(10Krows), Medium(10-1M rows), or large (1m+ rows)?  
    - The size of a data analysis project might influence the language a person tends to use because of differences in speed and efficiency.
3. Which language do you think has better documentation when it comes to its data analysis packages?  
    - Having clear and concise documentation aids in the ease of wrangling data and decreases the learning curve of the language. The user might tend to prefer the language they believe has better documentation.  
    
### Exploratory Data Analysis  

```{r, load_clean_data, include=FALSE}
# Import data
raw <- read_csv("https://raw.github.ubc.ca/MDS-2018-19/DSCI_554_R2Py2_results/master/DSCI_554_R2Py2.csv?token=AAAGaBhZe0kKbU2TUsf0Zd5rY6KxyKDuks5cuz3vwA%3D%3D")


# Data wrangle 
survey <- raw %>% 
  slice(-c(1:2)) %>% 
  select(contains("Q")) %>% 
  mutate(Q4=str_extract(Q4, "(^[A-Za-z]+)")) %>% 
  mutate(Q1 = as.factor(Q1),
         Q2 = as.factor(Q2),
         Q3 = as.factor(Q3),
         Q4 = as.factor(Q4),
         Q5 = as.factor(Q5))

survey <- as.data.frame(survey)
```  

##### Summary of survey results:  

```{r summary, echo=FALSE}
survey_summary <- summary(survey)
survey_summary
```  


```{r preferredLang, echo = FALSE}
#plots
plot1<-survey %>% ggplot(aes(x = Q1)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), width = 0.5, fill = 'salmon') +
  geom_text(aes(y = ((..count..)/sum(..count..)),
                label = scales::percent((..count..)/sum(..count..))),
            stat = "count", vjust = -0.25, width = 0.5) +
  theme_bw() +
  labs(title = 'Which Language is more prefered for Data Analysis?',
       x = 'Language',
       y='%') 
plot1
```  

65% of respondents preferred using Python vs R for data analysis. More people prefer python.  

```{r firstLang, echo=FALSE}
plot2<- ggplot(survey, aes(x=Q2, y=Q1) ) +
  geom_bin2d() +
  facet_grid(~Q5)+
  theme_bw() +
  labs(title = "First computing language you learned", 
      subtitle = 'Grouped by language with better documented packages',
       x = 'Language',
       y = 'Preference')
plot2
	
```

Those that learned a `dev_lang` (contains C/C++/C#/Java/Javascript) seem to almost always prefer python over R. Majority of the survey respondents were split between those that learned Python and `web_dev_lang` languages first first. As this heatmap was faceted with which language people believe have vetter documentation, this seems to show that more people prefer the language they believe have better documentation (the majority in this case, is Python).

```{r undergrad, echo=FALSE}
plot3<- ggplot(survey, aes(x=Q3, y=Q1) ) +
  geom_bin2d() +
  theme_bw() +
  labs(title = "What is your undergraduate degree in?",
       x = 'Major',
       y = 'Preference')
plot3

```  

Those with a Business, Math/Statistics/ or Computer Science background always prefer Python, those with Sciences/Other degrees seem to prefer R over Python. 

```{r size, echo=FALSE}
plot4<-survey %>% ggplot(aes(x = Q4)) +
  geom_bar(aes(fill = Q1), stat = 'count') +
  theme_bw() +
  scale_fill_discrete("Prefers:") +
  labs(title = "What is the size of your typical data set?",
       x = 'Size',
       y = 'Count')
plot4
```  

It seems more people prefer python no matter the size of the data set

```{r docs, echo=FALSE}
plot5<-survey %>% ggplot(aes(x = Q5)) +
  geom_bar(aes(fill = Q1), stat = 'count') +
  theme_bw() +
  scale_fill_discrete("Prefers:") +
  labs(title = "Which language has better documentation of data analysis packages??",
       x = 'Language',
       y = 'Count')
plot5
```

It seems highly correlated that people prefer to choose the language that they believe has better documentation. Over half of the respondents had experience with small analysis projects.

### Analysis  

```{r Analysis, echo=FALSE}

dev_langs = c("C/C++/C#", "Java/JavaScript")
web_dev_langs = c("HTML/XML/CSS", "Visual Basic/VBA", "SQL")

survey <- survey %>% 
  mutate(Q2 = ifelse(Q2 %in% dev_langs, "dev_lang", ifelse(Q2 %in% web_dev_langs, "web_dev_lang", as.character(Q2)))) %>% 
  mutate(Q3 = ifelse(Q3 == "Other Science", "Other", as.character(Q3))) %>% 
  mutate(Q2 = as.factor(Q2)) %>% 
  mutate(Q3 = as.factor(Q3))


log_reg <- glm(Q1 ~ Q2 + Q5 , family = "binomial", data = survey)
log_reg %>% tidy()
```  

### Discussion of Results  
**TODO**  

### Discussion of Survey  
**TODO**

